Place of death in NRS COVID-19 deaths: visualisation for 2022 data

### 2022-02-18 covid_nrs_place_of_death_visualisations_2022.Rmd
added reminder to myself

```{r}
figure_cause_of_death_annual_proportion_by_place <-
  current_and_historical_deaths_by_cause_and_location %>%
  filter(!cause_of_death %in% c("All")) %>%
  mutate(place_of_death = factor(place_of_death, levels = c("Hospital", "Home & other non-institution", "Care home", "Other"))) %>%  # needs to be factor with same levels, otherwise it messes up level order when added as geom_text later!)
  # mutate(
  #  cause_of_death = factor(cause_of_death %>% str_wrap(., width = 15), levels = order_of_causes_of_death %>% str_wrap(., width = 15)),  # needed to allow converting to a number for plotting the line segments; str_wrap breaks the text up into lines
  # ) %>%
  ggplot(aes(x = year, y = proportion, colour = place_of_death, group = place_of_death)) +
  geom_line() +
  geom_point() +
  facet_rep_wrap(~cause_of_death, repeat.tick.labels = TRUE) +
  scale_colour_viridis_d() +
  scale_y_continuous(labels = function(x) scales::percent(x, accuracy = 1)) +
  labs(
    x = "Year",
    y = "Percentage yearly deaths (%)",
    title = "In 2020 and 2021 the share of deaths at <b style='color:#31688E;'>Home</b> increased for all causes.\nDuring the pandemic, more cancer deaths happened at <b style='color:#31688E;'>Home</b> than in <b style='color:#440154;'>Hospital</b>.",
    subtitle = date_range_text,
    caption = paste0(c("The 2015-2019 number of deaths is the annual mean for the period.",source_nrs_text), collapse = "\n")
  ) +
  theme(
    panel.spacing = unit(1, units = "lines"),
    legend.position = "top", legend.title = element_blank(),
    plot.title = element_textbox_simple()  # to render the html in the title
    ) +
  guides(colour = guide_legend(nrow=2)) +  # spread colour legend over two rows
  NULL

>>>>

```{r}
# TODO: fix causes of deaths and reorder by number of deaths!
figure_cause_of_death_annual_proportion_by_place <-
  current_and_historical_deaths_by_cause_and_location %>%
  filter(!cause_of_death %in% c("All")) %>%
  mutate(place_of_death = factor(place_of_death, levels = c("Hospital", "Home & other non-institution", "Care home", "Other"))) %>%  # needs to be factor with same levels, otherwise it messes up level order when added as geom_text later!)
  # mutate(
  #  cause_of_death = factor(cause_of_death %>% str_wrap(., width = 15), levels = order_of_causes_of_death %>% str_wrap(., width = 15)),  # needed to allow converting to a number for plotting the line segments; str_wrap breaks the text up into lines
  # ) %>%
  ggplot(aes(x = year, y = proportion, colour = place_of_death, group = place_of_death)) +
  geom_line() +
  geom_point() +
  facet_rep_wrap(~cause_of_death, repeat.tick.labels = TRUE) +
  scale_colour_viridis_d() +
  scale_y_continuous(labels = function(x) scales::percent(x, accuracy = 1)) +
  labs(
    x = "Year",
    y = "Percentage yearly deaths (%)",
    title = "In 2020 and 2021 the share of deaths at <b style='color:#31688E;'>Home</b> increased for all causes.\nDuring the pandemic, more cancer deaths happened at <b style='color:#31688E;'>Home</b> than in <b style='color:#440154;'>Hospital</b>.",
    subtitle = date_range_text,
    caption = paste0(c("The 2015-2019 number of deaths is the annual mean for the period.",source_nrs_text), collapse = "\n")
  ) +
  theme(
    panel.spacing = unit(1, units = "lines"),
    legend.position = "top", legend.title = element_blank(),
    plot.title = element_textbox_simple()  # to render the html in the title
    ) +
  guides(colour = guide_legend(nrow=2)) +  # spread colour legend over two rows
  NULL
